% resume.tex
%
% This is the definitive source code of my resume, all of the other
% files in this folder are compiled from it.

\documentclass[11pt,a4paper,sans,colorlinks,urlcolor=blue]{moderncv}
\moderncvstyle{banking} % style options: 'casual', 'classic', 'oldstyle', 'banking'
\moderncvcolor{blue}
\usepackage[scale=0.75]{geometry} % adjust the page margins


% PERSONAL DATA

\name{Christopher}{Mazzullo}
\phone{(202)~253~1258}
\email{chris.mazzullo@gmail.com}
\homepage{github.com/cmazzullo}


% CONTENT

\begin{document}

\makecvtitle


\section{Experience}

\cventry{May 2017--Present}{Software Engineer}{IMS, Inc.}{Calverton, MD}{}{
  \begin{itemize}
  \item Developed and iterated on websites serving healthcare datasets
    to researchers including
    % Wrap links in \mbox to prevent line breaks inside them
    \mbox{\href{biolincc.nhlbi.nih.gov}{biolincc.nhlbi.nih.gov}},
    \mbox{\href{repository.niddk.nih.gov}{repository.niddk.nih.gov}}
    and \mbox{\href{neurobiobank.nih.gov}{neurobiobank.nih.gov}} in a
    small team setting (2-3 person) using a stack based on Django,
    Elasticsearch, and PostgreSQL.
  \item Developed a report combining information from internal
    databases with data from several REST APIs to decrease the
    workload of internal analysts by tracking the progress of requests
    through their lifecycle.
  \item Led the conversion of two roughly 50 KLOC codebases
    (\mbox{\href{biolincc.nhlbi.nih.gov}{biolincc.nhlbi.nih.gov}} and
    \mbox{\href{repository.niddk.nih.gov}{repository.niddk.nih.gov}})
    from Python 2 to Python 3.
  \item Started a series of internal technical talks to help
    cross-pollinate ideas about new approaches and technologies among
    IMS's engineers.
  \item Guided new features all the way from requirements-gathering
    with customers through implementation, testing and release.
  \end{itemize}
}

\cventry{Sept 2015--Nov 2016}{Software Engineer}{US Naval Observatory}{Washington, DC}{}{
  \begin{itemize}
  \item Rewrote a codebase responsible for computing Earth orientation
    parameters in Python, developing error metrics to gauge the
    accuracy of the new method.  These orientation parameters are used
    to improve the accuracy of both government and civilian GPS
    systems.
  \item Updated the public facing websites of the Earth Orientation
    division at USNO, and automated processes using Python and Bash to
    generate its data products.
\end{itemize}}

\cventry{June 2014--Sep 2015}{Software Engineer}{US Geological Survey}{Reston, VA}{}{
  \begin{itemize}
  \item Developed a Python application to clean, interpret and
    visualize large NetCDF files of raw data from pressure sensors
    showing trends in wave height and frequency on the Atlantic coast
    using a Scipy stack (numpy, matplotlib and pandas), as part of a
    2-person team.
  \item Designed algorithms using Fourier analysis to convert pressure
    data to wave height and frequency statistics for use in the
    application, repository available here:
    \mbox{\href{http://github.com/cmazzullo/wave-sensor}{github.com/cmazzullo/wave-sensor}}.
\end{itemize}}

\cventry{May 2014--May 2015}{Undergraduate Researcher}{George Mason University}{Fairfax, VA}{}{
  \begin{itemize}
  \item Developed software in IDL to analyze and visualize solar data
    from the Hinode satellite with funding from the Undergraduate
    Research Scholars Program, an internal grant at Mason.
  \item Investigated the velocity of plasma in coronal loops to help
    discriminate between different models of coronal heating, and
    presented the research at the 2015 National Conference on
    Undergraduate Research.
\end{itemize}}


\section{Volunteering}
\begin{itemize}
\item
  I work with the organization Code for DC building a React
  application to help pro-bono attorneys navigate the (convoluted) DC
  record expungement process:\\
  \mbox{\href{http://github.com/codefordc/rfj_expungement}{github.com/codefordc/rfj\_expungement}}.
\end{itemize}


\section{Education}
\cventry{May 2015}{\emph{BS} Physics, Minor Computer Science}{George Mason University}{Fairfax, VA}{}{}

\end{document}
